\section{Backend Structure}

The backend is implemented in TypeScript using a modular, Domain-Driven Design (DDD) approach built on a NestJS-style module pattern. The codebase is organized to reflect clear bounded contexts, a shared kernel for cross-cutting concerns, and an internals layer for platform services and infrastructure. This separation improves maintainability, testability, and team ownership.

\subsection{Architecture Overview}

At the highest level, the project is split into three logical layers:

\begin{enumerate}
	\item \textbf{Domain Layer}
	\item \textbf{Shared / Kernel Layer}
	\item \textbf{Internals / Infrastructure Layer}
\end{enumerate}

\subsection{Domain Layer}

This layer contains the core business logic and domain models, organized by bounded contexts under \texttt{domains}.

Each domain (for example: \texttt{auth}, \texttt{problem}, \texttt{submission}, \texttt{thread}, \texttt{user}) typically includes:

\begin{itemize}
	\item Controllers
	\item Services (use-case / application services)
	\item DTOs (Data Transfer Objects)
	\item Mappers
	\item Interfaces
	\item Domain-specific utilities
\end{itemize}

\subsection{Shared / Kernel Layer}

The shared layer contains reusable, domain-agnostic building blocks under \texttt{shared} and acts as a shared kernel to ensure reuse while keeping domain logic decoupled from framework specifics.

It includes:

\begin{itemize}
	\item Aggregate root patterns (e.g. \texttt{shared/aggregate})
	\item Base entities (e.g. \texttt{shared/entity})
	\item Common exceptions and constants
	\item Generic mappers
\end{itemize}

\subsection{Internals / Infrastructure Layer}

This layer contains platform-level concerns and infrastructure adapters under \texttt{internals}.

Common responsibilities:

\begin{itemize}
	\item Configuration (for example, \texttt{configuration.ts})
	\item Database setup and entity wiring (\texttt{database})
	\item Core framework services (\texttt{core})
	\item Infrastructure integrations (message brokers, external systems)
\end{itemize}

\subsection{Bounded Contexts and Module Responsibilities}

Each domain module represents a bounded context with clear ownership of its business logic.

\subsubsection{Auth Module}
\begin{itemize}
    \item Register and authenticate users (sign-up / sign-in).
    \item Issue, refresh, and revoke tokens / sessions.
    \item Validate and authorize requests based on roles/permissions.
    \item Enforce authentication-related business rules (e.g., account linking, password policies).
\end{itemize}


\subsubsection{Chatbot Module}
\begin{itemize}
    \item Intended to handle CRUD for AI conversation lifecycle (messages, sessions, histories).
    \item Acts as an adapter between HTTP controllers and an AI agent service (conversation orchestration).
    \item Stores or references conversation state and metadata for retrieval and continuation.
    \item Handle async processing and retries for AI responses.
    \item Integrates with infrastructure for calling external AI APIs and with message brokers for async tasks.
\end{itemize}

\subsubsection{Problem Module}
\begin{itemize}
    \item Create, update, publish, and archive problems.
    \item Manage problem metadata (tags, testcases, difficulty, reviews).
    \item Provide read models for public consumption and management views for editors.
    \item Validate problem inputs and maintain consistency of testcases and constraints.
\end{itemize}

\subsubsection{Submission Module}
\begin{itemize}
    \item Accept and record solution submissions from users.
    \item Queue and coordinate evaluation / judging workflows.
    \item Store and expose submission results, logs, and execution metadata.
    \item Handle retries, timeouts, and result aggregation for judging.
\end{itemize}

\subsubsection{Thread Module}
\begin{itemize}
    \item Create and manage discussions and comment threads.
    \item Support reactions/likes and moderation actions (edit/delete/report).
    \item Query and paginate discussions, comments, and thread metadata.
    \item Enforce posting rules and notification triggers for thread activity.
\end{itemize}

\subsubsection{User Module}
\begin{itemize}
    \item Manage user profiles, settings, and preferences.
    \item Handle user registration, authentication, and authorization.
    \item Provide user listing, search, and administrative controls.
    \item Enforce privacy, role-based access, and moderation policies.
\end{itemize}

\break