\section{System Evaluation}

System evaluation is conducted to verify that the implemented system satisfies the main functional requirements and provides an acceptable level of reliability, maintainability, and user experience. For CodeRank, the evaluation focuses on three main aspects: unit testing for backend and frontend logic, code coverage analysis using the V8 coverage provider, and frontend quality evaluation using Lighthouse. These evaluation methods are selected because they cover both internal implementation correctness and external user-facing quality.

\subsection{Unit Testing Strategy}

Unit testing is used to validate individual modules of the system in isolation. Instead of testing the whole application through the user interface, unit tests focus on smaller software units such as services, controllers, hooks, utility functions, and data transformation logic. This approach helps detect defects early and makes the implementation more maintainable because developers can verify whether a modification breaks existing behavior.

For the backend, Jest is used as the main testing framework. The backend is implemented with NestJS, and its modular structure allows domain services and controllers to be tested independently. The unit tests cover important business logic such as authentication, user management, problem management, problem request review, and submission status updates. Mock repositories and mocked service dependencies are used to isolate each unit from external systems such as the database and message broker.

For the frontend, Vitest is used as the testing framework. It is suitable for Vite-based React applications and supports fast execution in a JavaScript runtime environment. Frontend unit tests focus on reusable logic, service functions, route behavior, state management, form validation, and selected UI components. Since frontend behavior often depends on API responses, mock data and mocked HTTP clients are used to test components without requiring a live backend service.

The testing commands used in the project are shown below:

\begin{itemize}
    \item Backend unit testing: \texttt{npm run test}
    \item Backend coverage testing: \texttt{npm run test:coverage}
    \item Frontend unit testing: \texttt{npm run test}
    \item Frontend coverage testing: \texttt{npm run test:coverage}
\end{itemize}

\subsection{V8 Coverage and Branch Coverage}

Code coverage is used to measure how much of the source code is executed by the automated test suite. The project uses the V8 coverage provider for JavaScript and TypeScript tests. V8 is Google's open-source JavaScript and WebAssembly engine used by Chrome and Node.js \cite{v8docs2026}. The V8 coverage provider collects coverage information directly from the JavaScript runtime instead of requiring a separate source instrumentation step. Vitest supports native V8 coverage and notes that the V8 provider can execute source files without pre-instrumentation while still producing remapped coverage reports for source files \cite{vitest_coverage2026}.

Coverage is reported using four main metrics:

\begin{itemize}
    \item Statement coverage: measures how many executable statements are executed by tests.
    \item Line coverage: measures how many source lines are executed by tests.
    \item Function coverage: measures how many functions are called by tests.
    \item Branch coverage: measures how many decision paths are executed, such as \texttt{if}/\texttt{else}, conditional expressions, and switch cases.
\end{itemize}

Among these metrics, branch coverage is especially important for evaluating business logic. A function may be executed during testing, but only one branch of its decision logic may be covered. For example, a submission service may have separate paths for accepted submissions, wrong answers, runtime errors, and missing submissions. High branch coverage indicates that tests exercise more alternative paths and error cases, not only the successful path.

\subsection{Unit Testing Result}

The current coverage reports were generated from the existing backend and frontend test suites. Table \ref{tab:unit-test-coverage} summarizes the collected coverage results.

\begin{table}[H]
\centering
\caption{Unit Testing Coverage Result}
\label{tab:unit-test-coverage}
\begin{tabular}{|l|c|c|c|c|}
\hline
\textbf{Component} & \textbf{Statements} & \textbf{Branches} & \textbf{Functions} & \textbf{Lines} \\
\hline
Backend & 97.85\% & 90.05\% & 98.88\% & 97.85\% \\
\hline
Frontend & 49.84\% & 86.63\% & 88.63\% & 49.84\% \\
\hline
\end{tabular}
\end{table}

The backend coverage result is high across all measured categories. Statement coverage and line coverage both reach 97.85\%, function coverage reaches 98.88\%, and branch coverage reaches 90.05\%. This indicates that most backend service logic and important decision paths are exercised by the current test suite. The high branch coverage is particularly useful for backend validation because backend modules contain many conditional paths related to authentication, authorization, request validation, and domain state transitions.

The frontend result shows a different pattern. Function coverage reaches 88.63\% and branch coverage reaches 86.63\%, which indicates that many tested frontend functions and conditional paths are exercised. However, statement and line coverage are 49.84\%, showing that a significant amount of frontend source code is still not executed by the test suite. This is common in frontend projects when many pages, layout components, and UI states are implemented but not yet covered by component or integration tests. Therefore, frontend testing should be improved by adding tests for page-level components, form interactions, routing behavior, API error states, and authenticated user flows.

\subsection{Frontend Evaluation Using Lighthouse}

In addition to unit testing, the frontend was evaluated from the user's perspective using Lighthouse. Lighthouse is an open-source automated tool from Chrome for improving the quality of web pages. It audits several user-facing quality categories, including Performance, Accessibility, Best Practices, and SEO \cite{lighthouse2026}. These categories are useful for CodeRank because they measure not only whether the interface is functionally correct, but also whether it loads efficiently, follows accessibility expectations, avoids common browser-side issues, and provides basic metadata for search engines.

For this evaluation, the CodeRank frontend was built with Vite and served locally through the production preview server. The audit was executed on April 29, 2026 using Google Chrome in headless mode. Because the evaluation was performed on the local frontend preview rather than the deployed Vercel environment, the scores should be interpreted as a local baseline. Some API-dependent pages may report browser console errors when the backend service is not available, but the result is still useful for identifying frontend bundle, accessibility, and metadata issues before deployment.

The commands used to prepare and run the Lighthouse audit are shown below:

\begin{verbatim}
cd code-rank-web
./node_modules/.bin/vite build
./node_modules/.bin/vite preview --host 127.0.0.1 --port 4173
npx --yes lighthouse http://127.0.0.1:4173/auth/login \
  --chrome-path="/Applications/Google Chrome.app/Contents/MacOS/Google Chrome" \
  --chrome-flags="--headless --no-sandbox" \
  --only-categories=performance,accessibility,best-practices,seo \
  --form-factor=desktop \
  --output=json \
  --output-path=lighthouse-reports/login-desktop.json
\end{verbatim}

The same command was repeated for the selected pages and for both desktop and mobile form factors by changing the target URL and the \texttt{--form-factor} value. The evaluated pages were the login page, sign-up page, problem list page, problem detail page, and moderator dashboard. These pages were selected because they represent the main public, user-facing, problem-solving, and moderator workflows of the system.

\begin{table}[H]
\centering
\caption{Lighthouse Desktop Evaluation Result}
\label{tab:lighthouse-desktop-result}
\begin{tabular}{|l|c|c|c|c|}
\hline
\textbf{Page} & \textbf{Performance} & \textbf{Accessibility} & \textbf{Best Practices} & \textbf{SEO} \\
\hline
Login Page & 43 & 100 & 96 & 83 \\
\hline
Sign-up Page & 42 & 87 & 96 & 75 \\
\hline
Problem List Page & 35 & 93 & 96 & 83 \\
\hline
Problem Detail Page & 35 & 94 & 96 & 82 \\
\hline
Moderator Dashboard & 35 & 94 & 96 & 82 \\
\hline
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{Lighthouse Mobile Evaluation Result}
\label{tab:lighthouse-mobile-result}
\begin{tabular}{|l|c|c|c|c|}
\hline
\textbf{Page} & \textbf{Performance} & \textbf{Accessibility} & \textbf{Best Practices} & \textbf{SEO} \\
\hline
Login Page & 60 & 100 & 96 & 83 \\
\hline
Sign-up Page & 60 & 87 & 96 & 75 \\
\hline
Problem List Page & 56 & 93 & 96 & 83 \\
\hline
Problem Detail Page & 49 & 94 & 96 & 82 \\
\hline
Moderator Dashboard & 55 & 94 & 96 & 82 \\
\hline
\end{tabular}
\end{table}

The Lighthouse results show that CodeRank performs well in Best Practices, with all evaluated pages scoring 96. Accessibility is also strong on most pages, ranging from 93 to 100, although the sign-up page received a lower score of 87 because Lighthouse detected missing or insufficient accessible labels and image alternative text. SEO scores range from 75 to 83. The main SEO issue is the absence of complete page metadata, especially a meta description and route-specific document metadata.

Performance is the weakest category in the current frontend baseline. Desktop performance ranges from 35 to 43, while mobile performance ranges from 49 to 60. Lighthouse reported delayed First Contentful Paint and Largest Contentful Paint, moderate Total Blocking Time, and a high amount of unused JavaScript. During the Vite production build, the generated JavaScript bundle was approximately 2,328.95 KB before gzip compression and 684.81 KB after gzip compression. This confirms that the application currently ships a large initial bundle. The problem detail page is especially affected because it includes heavier problem-solving UI dependencies such as the code editor and markdown rendering.